Experiment

### 2021-04-17 analysis/experiment.Rmd
Use targets now!

---
title: "Experiment"
author: "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
    pandoc_args:
      - "--default-image-extension=png"
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Experiment"
author: "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---
